### 2019-08-21 Manuscript/Manuscript.tex

>>>>

\subsection*{Paleoshoreline data}

While the overall picture of the region is an increase in land area, there is a decrease in land area associated with subsidence of the Sunda Shelf. Although the majority of the Sunda Shelf is currently submerged, large portions of this low-relief area of continental crust were likely emergent throughout the Neogene, and were repeatedly subaerially exposed during the Pleistocene as recently as the Last Glacial Maximum \citep{Halls2002a}. Similarities in terrestrial biotas of Borneo and mainland Southeast Asia suggest the existence of land bridges on the Sunda Shelf throughout the Miocene \citep{Moss1998a}. During the Eocene through early Miocene, the rifting of the South China Sea resulted in subsidence throughout the Sunda Shelf \citep{Morley2013a}. In the Miocene, this region was likely a mixture of crystalline lithologies and siliciclastic sediments. This low-relief region contrasts with the high-relief and mafic lithologies of the broader Indonesia archipelago.
